Supplementary Material for Asymmetry paper

### 2020-06-11 Supplementary/Sup_mat.Rmd
New version of sup mat run
- All models have been rerun
- Need to add more text to talk about the priors etc. and figure captions

@@

``` {r}
options(mc.cores = parallel::detectCores())
```
# Power Analysis

@@

## Experiment 1: Two Hoop Sizes

```{r loaddata, include = T, echo = F, fig.height = 3}
# load("../power/Hoop_size/scratch/sampled_data")
# load("../power/Hoop_size/scratch/df_part2")
```

We started by fitting a a beta distribution to each participant's date from the _Throwing Experiment_ in @clarke2015failure using the `fitdistrplus` package (as can be seen in Figure \@ref(fig:drawdistributions). In the original data, normalised standing position was coded $\phi \in [0,1]$ with $0$ indicating a central standing position, and $1$ indicating the participant stood by either of the two hoops. As we are _breaking the symmetry_ between the two targets in this new experiment, we will now treat standing position as $\phi \in (0, 1)$ with $0$ and $1$ representing the positions of the large and small hoop respectively. The central midpoint is now represented as $\phi = 0.5$.

@@

# make some plots
df_dists <- tibble(Participant = rep(unique(df_distributions$participant), each = length(x) * length(mus)),
                   x_vals = rep(x, length(mus) *length(unique(df_distributions$participant))),
                   increase = rep(rep(mus, each = length(x)), length(unique(df_distributions$participant))),
                   alpha = rep(unique(df_distributions$alpha), each = length(x)),
                   beta = rep(unique(df_distributions$beta), each = length(x))) %>% 
  mutate(increase = as.factor(increase)) %>% 
  group_by(Participant, increase, x_vals) %>% 
  mutate(y = dbeta(x_vals, alpha, beta))

@@

# load data
# load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")

@@

*What about the split in reward???*

## Experiment 4: Probability Matching
```{r load data, include = F, echo = F, message = F, warning = F}
load("../power/Prob_match/scratch/df_resample")
load("../power/Prob_match/scratch/df_sample")
```

@@

```{r, echo - FALSE}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

@@

@@

### Prior Predictive Check

@@

```{r run-model-hoop-size-priors, echo = F, include = F, cache = TRUE}

@@

```{r HoopSizePriors, include = T, echo = F, warning = F,  fig.asp = .45, fig.cap="_Prior predictive Check for the Hoop Size experiment_"}
# need to make a dataset
draws <- HS_draw_post(Hoop_size_priors, model_data)

@@

```{r run-model-Hoop-size, include = F, echo = F, cache = TRUE}

@@

@@

```{r Two_Throws_Priors_only_model, include = F, echo = F, cache = T}

@@

```{r PltTwoThrowPriors, include = T, echo = F, fig.asp=.45, fig.cap="_Prior predictive Check for the Two Throw Experiment_"}
# get draws 
draws_df <- draw_post_delta(Two_throw_priors, model_data_pos)

@@

```{r Two-throws modelling, include = F, echo = F, cache = T}

@@

A Bayesian Beta Regression was carried out in order to investigate whether opting for an unequal reward structure in this task would facilitate the use of a more optimal strategy in the _Throwing Task_. The predictors in this model were whether the participant had opted for an _Equal_ or _Unequal_ (Gamble_Type), whether the hoops were _Close_ or _Far_ (dist_type), and the interaction between these. Additionally, random effects of participant were included for all predictors. The predicted value was the normalised standing position, with 0 representing the centre and 1 being next to one of the hoops.  
```{r GamblingPriorsOnly, include = F, echo = F, warning = F, cache = T}
Reward_priors <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type * Gamble_Type|Participant),
                     data = model_data,
                     family = "beta",
                     prior = c(set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar:Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,1)",
                                         class = "Intercept")),
                     chains = 1,
                     iter = 10000,
                     warmup = 5000,
                     sample_prior = "only",
                     control = list(adapt_delta = .99, max_treedepth = 15))
```

``` {r RewardPriorsPlt, include = T, echo = F, fig.asp = .45, fig.cap = "_Prior predictive Check for the Reward Study_"}
draws_factor(Reward_priors) %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop,
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  geom_density(alpha = .3,
               kernel = "biweight") +
  scale_x_continuous(expression(paste("Normalised ", Delta))) +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  facet_wrap(~Dist_Type) + 
  theme_bw()
```

@@

```{r RewardModel, include = F, echo = F, warning = F, cache = T}
# run model 
Reward_m1 <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type*Gamble_Type|Participant),
                 data = model_data,
                 family = "beta",
                 prior = c(set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "dist_typefar"),
                           set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "dist_typefar:Gamble_TypeUnequal"),
                           set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "Gamble_TypeUnequal"),
                           set_prior("student_t(3,0,1)",
                                     class = "Intercept")),
                 chains = 1,
                 iter = 10000,
                 warmup = 5000,
                 control = list(adapt_delta = .99, max_treedepth = 15))

@@

### _Participants_
16 Particiapnts (two Male) were recruited from the University of Aberdeen community with an average age of 22.75 (between 19 and 29). Each participant was reimbursed £10 for their time.

### _Procedure_
The experiment followed a similar procedure to the "_Detection Task_" from @clarke2015failure. In the first session, we measured visual acuity which lasted approximately 30 minutes. This was followed by a second session in which the participants performed the actual decision task which lasted approximately 40-50 minutes.

@@

### Analysis

All analysis for this experiment follow the same procedures as described in previous sections.

## Results

```{r Probability, include = F, echo = F}
# Load in everything from the modelling
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt")
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt_draws")
draws <- fix_like_post$draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  select(-estimate)
```

```{r ProbProp, include = T, echo = F, fig.asp=.45, fig.cap="_These boxplots show the proportion of the time that participants fixated the centre (left panel), most-likely (central panel) and least-likely (right panel) box. In the _Bias_ condition, 'most likely' was the box with and 80% probability of containing the target. In the _Symmetric_ condition, 'most-likely' was whichever side box a given participant had fixated the most. The Close and Far distinction is baseed on when participants should swith from fixating the central box to the side box. Note that for some participants, expected performance differences between the Centre and Side strategies for the closest separation was negligible. However, all participants should have fixated the Side boxes in the Far condition, where the performance advantage of doing so was substantial._"}

#knitr::include_graphics('../Figures/Experiment_4_Prob/boxes_prop_CML.png')
plt_prop_fix <- readPNG("../Figures/Experiment_4_Prob/boxes_prop_CML.png")
grid.raster(plt_prop_fix)

@@

### Modelling 
```{r Get Values, include = F, echo = F}
# HDI_values 
HDI_Bias <- draws %>%
  group_by(Bias_type) %>%
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))
HDI_Dist <- draws %>% 
  group_by(Dist_type) %>% 
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))
HDI_interaction <- draws %>% 
  group_by(Bias_type, Dist_type) %>% 
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))

@@

plt_interaction <- fix_like_post$plt_estimates +
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  labs(x = "Proportion of Fixations to Most Likely Side",
       colour = "Bias Type",
       fill = "Bias Type") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

gridExtra::grid.arrange(plt_me_Dist, plt_me_Bias, plt_interaction)
```

>>>>

```{r settings, include = F, echo = F}
knitr::opts_chunk$set(fig.align = "center")
```

@@

``` {r, echo = F, include = F}
options(mc.cores = parallel::detectCores())
```
# Power Analysis

@@

## Experiment 1: Two Hoop Sizes
We started by fitting a a beta distribution to each participant's date from the _Throwing Experiment_ in @clarke2015failure using the `fitdistrplus` package (as can be seen in Figure \@ref(fig:drawdistributions). In the original data, normalised standing position was coded $\phi \in [0,1]$ with $0$ indicating a central standing position, and $1$ indicating the participant stood by either of the two hoops. As we are _breaking the symmetry_ between the two targets in this new experiment, we will now treat standing position as $\phi \in (0, 1)$ with $0$ and $1$ representing the positions of the large and small hoop respectively. The central midpoint is now represented as $\phi = 0.5$.

@@

# make some plots
df_dists <- tibble(Participant = rep(unique(df_distributions$participant), each = length(x) * length(mus)),
                   x_vals = rep(x, length(mus) *length(unique(df_distributions$participant))),
                   increase = rep(rep(mus, each = length(x)), length(unique(df_distributions$participant))),
                   alpha = rep(unique(df_distributions$alpha), each = length(x)),
                   beta = rep(unique(df_distributions$beta), each = length(x))) %>% 
  mutate(increase = as.factor(increase)) %>% 
  group_by(Participant, increase, x_vals) %>% 
  mutate(y = dbeta(x_vals, alpha, beta)) %>% 
  filter(increase %in% c(0, .05))

@@

# load data
load("../power/Money_and_two/scratch/df_all")

@@

## Experiment 4: Probability Matching
```{r load data, include = F, echo = F, message = F, warning = F}
load("../power/Prob_match/scratch/df_resample")
```

@@

```{r load data and source function Hoop Size, echo - FALSE}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

@@

Add in facet plots

```{r HoopSizeFacets, include=T, echo=F}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

# process data 
df_hoopsize %>% 
  group_by(participant) %>% 
  mutate(temp = as.numeric(as.factor(hoop_pos)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>%
  ungroup() %>% 
  filter(abs(norm_dist) <= 1) %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(hoop_pos))-> df_hoopsize

# make plot
df_hoopsize %>% 
  ggplot(aes(overall_hoop_pos, norm_dist)) + 
  geom_jitter(alpha = .2,
              width = .2,
              height = .2) +
  facet_wrap(~participant, ncol = 3) + 
  geom_hline(yintercept = 0, 
             linetype = "dashed") +
  scale_y_continuous("", 
                     breaks = c(-1, 0, 1),
                     labels = c("Big Hoop", "Centre", "Small Hoop")) +
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")")),
                     expand = c(0.1,0.1),
                     breaks = unique(df_hoopsize$overall_hoop_pos),
                     labels = c("-1", "0", "+1", "+2", "F", "C")) +
  theme_bw() + 
  theme(strip.text.x = element_blank(),
        panel.grid.minor = element_blank())

@@

### Prior Predictions

@@

```{r run-model-hoop-size-priors, echo = T, include = F, cache = TRUE}

@@

```{r HoopSizePriors, include = T, echo = F, warning = F,  fig.asp = .45, fig.cap="_Prior predictions for the Hoop Size experiment_"}
# need to make a dataset
draws <- HS_draw_post(Hoop_size_priors, model_data)

@@

```{r run-model-Hoop-size, include = F, echo = T, cache = TRUE}

@@

Add in facet plot

``` {r TwoThrowFacets, include = T, echo = F}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

# make plot 
df_TwoThrow %>% 
  ggplot(aes(overall_hoop_pos, abspos,
             colour = Num_throws)) + 
  geom_jitter(alpha = .2,
              width = .2) + 
  facet_wrap(~Participant, ncol = 6) + 
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")")),
                     breaks = unique(df_TwoThrow$overall_hoop_pos),
                     labels = c("C", "+1","-1", "+2", "0", "F")) +
  scale_y_continuous("",
                     breaks = c(0,1),
                     labels = c("Centre", "Side")) +
  see::scale_color_flat() +
  theme_bw() + 
  guides(fill = guide_legend("No. Throws")) +
  theme(strip.text.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 8),
        legend.position = "bottom")

@@

```{r Two_Throws_Priors_only_model, include = F, echo = T, cache = T}

@@

```{r PltTwoThrowPriors, include = T, echo = F, fig.asp=.45, fig.cap="_Prior Predictions for the Two Throw Experiment_"}
# get draws 
draws_df <- draw_post_delta(Two_throw_priors, model_data_pos)

@@

```{r Two-throws modelling, include = F, echo = T, cache = T}

@@

Add in facets

``` {r RewardFacets, include = T, echo = F}
df_Rewards <- model_data %>%
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(Norm_Delta)),
         slab_measures = factor(temp, labels = c("90%", "75%", "25%", "10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(Norm_Delta))

df_Rewards %>% 
  ggplot(aes(overall_hoop_pos, Norm_Dist,
             colour = Gamble_Type)) + 
  geom_jitter(alpha = .3,
              width = .05,
              height = .05) +
  facet_wrap(~Participant, ncol = 4) + 
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")")),
                     breaks = unique(df_Rewards$overall_hoop_pos),
                     labels = unique(df_Rewards$slab_measures)) +
  scale_y_continuous("",
                     breaks = c(0,1),
                     labels = c("Centre", "Side")) +
  see::scale_color_flat() +
  theme_bw() + 
  theme(
    strip.text.x = element_blank(),
    legend.position = "bottom",
    axis.text.x = element_text(size = 8),
    panel.grid.minor.x = element_blank()
  )

A Bayesian Beta Regression was carried out in order to investigate whether opting for an unequal reward structure in this task would facilitate the use of a more optimal strategy in the _Throwing Task_. The predictors in this model were whether the participant had opted for an _Equal_ or _Unequal_ (Gamble_Type), whether the hoops were _Close_ or _Far_ (dist_type), and the interaction between these. Additionally, random effects of participant were included for all predictors. The predicted value was the normalised standing position, with 0 representing the centre and 1 being next to one of the hoops.  
```{r GamblingPriorsOnly, include = F, echo = T, warning = F, cache = T}
Reward_priors <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type * Gamble_Type|Participant),
                     data = model_data,
                     family = "beta",
                     prior = c(set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar:Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,1)",
                                         class = "Intercept")),
                     chains = 1,
                     iter = 10000,
                     warmup = 5000,
                     sample_prior = "only",
                     control = list(adapt_delta = .99, max_treedepth = 15))
```

``` {r RewardPriorsPlt, include = T, echo = F, fig.asp = .45, fig.cap = "_Prior Predictions for the Reward Study_"}
draws_factor(Reward_priors) %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop,
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  geom_density(alpha = .3,
               kernel = "biweight") +
  scale_x_continuous(expression(paste("Normalised ", Delta))) +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  facet_wrap(~Dist_Type) + 
  theme_bw()
```

@@

```{r RewardModel, include = F, echo = T, warning = F, cache = T}
# run model 
Reward_m1 <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type*Gamble_Type|Participant),
                 data = model_data,
                 family = "beta",
                 prior = c(set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "dist_typefar"),
                           set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "dist_typefar:Gamble_TypeUnequal"),
                           set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "Gamble_TypeUnequal"),
                           set_prior("student_t(3,0,1)",
                                     class = "Intercept")),
                 chains = 1,
                 iter = 10000,
                 warmup = 5000,
                 control = list(adapt_delta = .99, max_treedepth = 15))

@@

### Participants
16 Particiapnts (two Male) were recruited from the University of Aberdeen community with an average age of 22.75 (between 19 and 29). Each participant was reimbursed £10 for their time.

### Procedure
The experiment followed a similar procedure to the "_Detection Task_" from @clarke2015failure. In the first session, we measured visual acuity which lasted approximately 30 minutes. This was followed by a second session in which the participants performed the actual decision task which lasted approximately 40-50 minutes.

@@

### Analysis
All analysis for this experiment follow the same procedures as described in previous sections.

## Results
```{r ProbProp, include = T, echo = F, fig.asp=.45, fig.cap="_These boxplots show the proportion of the time that participants fixated the centre (left panel), most-likely (central panel) and least-likely (right panel) box. In the _Bias_ condition, 'most likely' was the box with and 80% probability of containing the target. In the _Symmetric_ condition, 'most-likely' was whichever side box a given participant had fixated the most. The Close and Far distinction is baseed on when participants should swith from fixating the central box to the side box. Note that for some participants, expected performance differences between the Centre and Side strategies for the closest separation was negligible. However, all participants should have fixated the Side boxes in the Far condition, where the performance advantage of doing so was substantial._"}

plt_prop_fix <- readPNG("../Figures/Experiment_4_Prob/boxes_prop_CML.png")
grid.raster(plt_prop_fix)

@@

### Modelling
#### Prior Predictive checks
```{r Prob load data, include = F, echo = F}
# load data
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_data/df_model")

# load function
source("extract_draws_functions/Prob_draws.R")

n_iter <- 2000
n_warmup <- n_iter/2
```

``` {r Setting Priors, include = F, echo = T}
# setting priors
Rewards_priors <- c(set_prior("student_t(3, 0, .5)", class = "b"),
                    set_prior("student_t(3, 0, .5)", class = "b", coef = "bias_typeSymmetric"),
                    set_prior("student_t(3, 0, .5)", class = "b", coef = "bias_typeSymmetric:dist_typeFar"),
                    set_prior("student_t(3, 0, .5)", class = "b", coef = "dist_typeFar"),
                    set_prior("student_t(3,0,1)", class = "Intercept"))
```

```{r ProbPriors, include = F, echo = T, cache = T}
ProbPriors_model <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                        data = df_model,
                        family = "bernoulli",
                        prior = Rewards_priors,
                        chains = 1,
                        iter =   n_iter,
                        warmup = n_warmup,
                        sample_prior = "only")
```

```{r ProbPriorsPlt, include = T, echo = F}
ProbPriordraws <- Prob_draws(ProbPriors_model)

plt_ProbPrior_interaction <- ProbPriordraws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  theme_bw() + 
  guides(fill = guide_legend("Bias Type"),
         colour = guide_legend("Bias Type"))

prior_draws <- ProbPriordraws$draws_df %>%
  mutate(prop = boot::inv.logit(estimate)) %>%
  select(-estimate)

plt_ProbPrior_meDist <- prior_draws %>%
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

plt_ProbPrior_meBias <- prior_draws %>%
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  theme(axis.title.x = element_blank()) +
  labs(fill = "Bias Type",
       colour = "Bias Type") +
  #       "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

gridExtra::grid.arrange(plt_ProbPrior_meDist, plt_ProbPrior_meBias, plt_ProbPrior_interaction)

```{r ProbModel, include = F, echo = T, cache = T}
ProbModel <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                 data = df_model,
                 family = "bernoulli",
                 prior = Rewards_priors,
                 chains = 1,
                 iter = n_iter,
                 warmup = n_warmup)
```

```{r ProbModelPlts, include = T, echo = F}
Probdraws <- Prob_draws(ProbModel)

plt_ProbPost <- Probdraws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  theme_bw() + 
  guides(fill = guide_legend("Bias Type"),
         colour = guide_legend("Bias Type"))
```

```{r Get Values, include = F, echo = F}
# get draws
draws <- Probdraws$draws_df %>%
  mutate(prop = boot::inv.logit(estimate)) %>%
  select(-estimate)

# HDI_values 
HDI_Bias <- draws %>%
  group_by(Bias_type) %>%
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))
HDI_Dist <- draws %>% 
  group_by(Dist_type) %>% 
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))
HDI_interaction <- draws %>% 
  group_by(Bias_type, Dist_type) %>% 
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))

@@

gridExtra::grid.arrange(plt_me_Dist, plt_me_Bias, plt_ProbPost)
```
